---
title: "Work in progress title for E= project"
author: "Alexander Park"
date: "2023-01-26"
output: 
  slidy_presentation: 
    fig_height: 3
    fig_width: 5
    smaller: yes
---
packages needed so far 
```{r}
library(tibble) # used to create tibbles
library(tidyr) # used to tidy up data
library(rmarkdown) # dynamic document 
library(ggplot2) # used for data visualization
library(dplyr) # used for data manipulation
library(shiny) # used for showing dynamic visuals in collaboration with ggvis
library(prettydoc)# used for creating pretty documents from R markdown
library(knitr)#for dynamic report generation
library(tidyverse)# multiple tidy up data packages here
library(hms) # used to install kableExtra package
library(kableExtra) # used to construct Complex Table for data
library(dplyr) # used to install tigris package
library(tigris) # used to make states map
#added library for other graphs
library(plotly)
library(rjson)
library(leaflet)
library(leaflet.providers)
library(maps)
library(viridis)
library(viridisLite)
library(sp)
library(quantmod)
library(sf)
library(RColorBrewer)
library(gganimate)
library(countrycode)

```

The big questions is what am I doing with this dataset and answering for. 
1st question I could explore is other types of Energy such as wind, solar, other renewable are better in terms of 
2nd. Is Renewable better than oil and gas in long term 
3rd. Are oil and gas energy levels higher than other renewable energy such solar, energy, 
4th, detail into the difference of energy consumption of wind, solar, other renewable resources. 
 a. Create a interactive bubble graph of countries that use the most renewable energy resource. 
5th. Visually show the difference of energy consumption between countries in renewable vs 
6th. Countries 

follow similarily to the tableau project but make it your own. Maybe go in details of the difference of wind, solar, some type of energy compared to oil and gas. Which countries are using which energy more. 


VISUAL REPRESENTATION 
1. create graphs of countries leaflet plotly of the percentile of most used energy used 
2. graphs bar graphs, 
3. bubble map 
4. maybe 3d graph 
5. interactive maps/ bubble map/ graphs/ 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# WIP Introduction 

- this introduction discusses the meta data of the two data sets from kaggle and what they are. 
- Explain the terms that might be unknown to people
- at the end briefly describe the big question that is gonna to be ask which is renewable vs non-renewable 

1. First question are what are the renewable energy consumptions and what are the non-renewable resources, Which countries are utilizes the most of which energy source, See which are oil, gas, then the renewable ones. 

link the two datasets here [] 

the first sets of visual graphs will display the dataset of the renewable sources vs the non-renewable in a dataframe that has been manupulated. 

Then display it by showing through leaflet map of countries, bubble map, discover new maps to use it for, use interactive things on R to visually show the energy consumptions levels, and the per capita level, then population


For the dataframe I need from the world dataset only I need columns of 
1. countries 
2. year 
3. 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

states <- states(cb = TRUE, class = "sf") %>% 
  filter(!as.numeric(STATEFP) %in% c(2, 15, 60, 66, 69, 72, 78)) %>%
  mutate(var = rnorm(nrow(.)))





library(plotly)

g <- list(
  projection = list(
    type = 'orthographic'
  ),
  showland = TRUE,
  landcolor = toRGB("#e5ecf6")
)

fig <- plot_ly(type = 'scattergeo', mode = 'markers')
fig <- fig %>% layout(geo = g)
fig
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
